%%%%%%%%%%%%%%%%%%%%%%%% referenc.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% sample references
% %
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%%%%%%%%%% Springer-Verlag %%%%%%%%%%%%%%%%%%%%%%%%%%
%
% BibTeX users please use
% \bibliographystyle{}
% \bibliography{}
%

\begin{thebibliography}{99.}%
% and use \bibitem to create references.
%
%
% Use the following syntax and markup for your references if 
% the subject of your book is from the field 
% "Computer Science, Economics, Engineering, Geosciences, Life Sciences"
%
%
\bibitem{Brown} Brown B, Aaron M (2001) The politics of nature. In: Smith J (ed) The rise of modern genomics, 3rd edn. Wiley, New York 

\bibitem{MG-RAST}F Meyer, D Paarmann, M D'Souza, R Olson, EM Glass, M Kubal, T Paczian, A Rodriguez, R Stevens, A Wilke, J Wilkening, RA Edwards (2008). The metagenomics RAST server – a public resource for the automatic phylogenetic and functional analysis of metagenomes. BMC Bioinofmatics. 9:386. doi:10.1186/1471-2105-9-386

\bibitem{Mason-deepwater} Mason, O., Hazen T., Borglin, S., Chain, P., Dubinsky, E., Fortney, J., et al. (2012). Metagenome, metatranscriptome and single-cell sequencing reveal microbial response to Deepwater Horizon oil spill. The ISME journal, 6(9), 1715-1727

\bibitem{Korenblum} Korenblum E., Souza DB., Penna M, Seldin L. (2013). Molecular Analysis of the Bacterial Communities in Crude Oil Samples from Two Brazilian Offshore Petroleum Platforms. International Journal of Microbiology Volume 2012. doi:10.1155/2012/156537
Lorenz P and Eck J. (2005). Metagenomics Industrial Applications. Nature Reviews Microbiology 3, 510-516. doi:10.1038/nrmicro1161

\bibitem{Hampton-Marcell} Hampton-Marcell JT., Moormann SM., Owens SM., Gilbert JA. (2013) Preparation and Metatranscriptomic Analyses of Host-Microbe Systems in Microbial Metatgenomics, Metatranscrtomics, and Metaproteomics volume 531 issue 169. Academic Press. ISBN 978-0-12-407863-5. ISSN 0076-6879.

\bibitem{Rubin} Rubin BER., Gibbons SM., Kennedy S., Hampton-Marcell J., Owens S., Gilbert J. (2013) Investigating the Impact of Storage Conditions on Microbial Community Composition in Soil Samples. PLOSone. DOI: 10.1371/journal.pone.0070460

\bibitem{Segata} Segata, N., Boernigen D., Tickle TL., Morgan XC., Garrett WS, Huttenhower C. (2013) Computational Meta’omics for Microbial Community Studies. Molecular Systems Biology, doi: 10.1038/msb.2013.22

\bibitem{MIE} Thomas, T., Gilbert, J., Meyer, F. (2012). Metagenomics – a guide from sampling to data analysis. Microbial Informatics and Experimentation, 2, doi:10.1186/2042-5783-2-3

\bibitem{Wang}Wang LY., Ke WJ., Sun XB., Liu JF., Gu JD., Mu BZ. (2013). Comparison of bacterial community in aqueous and oil phases of water-flooded petroleum reservoirs using pyrosequencing and clone library approaches. Appl Microbiol Biotechnol. DOI 10.1007/s00253-013-5472-y

\bibitem{API} A Wilke, J Bischof, T Harrison, T Brettin, M D'Souza, W Gerlach, HMatthews, T Paczian, J Wilkening, E M Glass, N Desai, F Meyer. (2015) A RESTful API for Accessing Microbial Community Data for MG-RAST. PLOS: Computational Biology. DOI: 10.1371/journal.pcbi.1004008
%
% Online Document
%\bibitem{basic-online} Dod J (1999) Effective Substances. In: The dictionary of substances and their effects. Royal Society of Chemistry. Available via DIALOG. \\
%\url{http://www.rsc.org/dose/title of subordinate document. Cited 15 Jan 1999}
%
% Journal article by DOI
%\bibitem{basic-DOI} Slifka MK, Whitton JL (2000) Clinical implications of dysregulated cytokine production. J Mol Med, doi: 10.1007/s001090000086
%
% Journal article
%\bibitem{basic-journal} Smith J, Jones M Jr, Houghton L et al (1999) Future of health insurance. N Engl J Med 965:325--329
%
% Monograph
%\bibitem{basic-mono} South J, Blass B (2001) The future of modern genomics. Blackwell, London 
%
\end{thebibliography}
